---
title: "Week 8, Day 2"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Recall that Enos (2014) actually looks at a measure of change in attitude
# toward immigration, rather than simply at the ending attitude. Let's create
# such a variable and try to model it.

week_8 <- trains %>% 
  mutate(att_chg = att_end - att_start) %>% 
  select(att_chg, gender, party, liberal, treatment)
  
```

Weeks 7, 8 and 9 are the core of the class. We have a question. We have some data. How should we use the data to answer the question? Using Wisdom, we first decide if the question and the data are "close enough" that we can consider them to both be part of the same population. With Justice, we create a mathematical model which describes the connection between the outcome we want to explain/understand an the covariates which might be connected to it. Courage takes us from mathematics to code, creating a model, including posterior distributions for all its parameters. The last step is to use that model to answer the question with which we started, with Temperance.

**Question:** *What would Preceptor's change in attitude toward immigration be if he were to receive the treatment next week?*

## Scene 1

**Prompt:** We have not practiced writing mathematical formulas in R markdown documents. Doing so is fairly simple. Bracket the math in one dollar sign if you want it to appear inline. Example: a y in math notation looks like $y$ and is produced with \$y\$. Subscripts require an underscore, and a bracket is often helpful. To make $y_i$ you write  \$y\_i\$. For $x_{t,i}$ write \$x\_{t, i}\$. To put the math on its own line, use two dollar signs. Here is a version of one of the formulas from chapter 8:

$$ age_i = \beta_1 x_{r,i} + \beta_2 x_{d,i} + \epsilon_i$$
Today, we will be considering `att_chg` as a function of `treatment`. 

* Create the mathematical formula for that model here.

$$ att_chg_i \beta_1 treated_i + \beta_2 control_i + \epsilon_i$$
-att_chg is dependent variable
-1 independent variable: treatment
-epsilon represents error

* Describe the ideal Preceptor Table.
-3 columns: ID, attitude change of treated group, attitude change of control 
group, ATE

* Write a few sentences about whether or not our data will allow us to answer this question.
The formula and data are generally able to model this, but it is difficult to
predict for a single individual. The data is from Boston commuters in 2012, and
immigration attitudes could have broadly changed over that time.


## Scene 2

**Prompt:** There are two ways to interpret our question. The first involves our expectation. We can also think of this as the long-term average, if we did the same experiment over and over again. (Assume that Preceptor is always assigned to the treatment.) What is your posterior probability distribution for Preceptor's *expected* `att_chg`?

```{r}
fit_obj <- stan_glm(data = week_8,
                    att_chg ~ treatment - 1,
                    refresh = 0)

fit_obj %>%
  as_tibble() %>%
  ggplot(aes(x = treatmentTreated)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
  labs(title = "Posterior Distribution for Attitude change of Preceptor")
  
posterior_interval(fit_obj, prob = .95)
#CI: (.0074, .7815)

```


## Scene 3

**Prompt:** The second way to interpret the question is with regard to a single individual. What will happen to Preceptor next week? Provide a Posterior Predictive Distribution for what you predict will be Preceptor's `att_chg` after treatment.

```{r}
fit_obj %>% 
  as_tibble() %>%
  select(treatmentTreated)
post <- posterior_predict(fit_obj))

post %>%
  as_tibble() %>%
  mutate(across(everything(), as.numeric)) %>%
  ggplot(aes(x = `1`)) + geom_histogram(bins = 100)
```


## Challenge Problem

Create the posterior distribution for the average treatment effect of `treatment` within subsets of the data defined by `liberal` and by `gender`.  In other words, there should be 4 plots total: `liberal == FALSE`, `liberal == TRUE`, `gender == "Male"` and `gender == "Female"`. Put all these posteriors in the same graphic. (One approach is to use the **patchwork** package.) The elegant approach is to create a function which takes a tibble and a restriction, and then returns the plot.



